Notes on conformal manifolds

### 2025-05-22 Draft_MLFlatDirections.tex
Update of the results section.

  \begin{enumerate}
  		\item For 100 runs with parameters
		\begin{equation} \label{eq:sample10000beta5}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 59\% & 25\% & 5\% & 9\% & 2\% & 4\% & 2\% & 13\%
	  	\end{tabular}
	  \end{equation}
	  The sum of the percentages is higher than 100\% because some runs find more than one polynomials. The code fails to find any polynomial in 13\% of the time. The averaged time needed for a single run on a PC in $\sim 700\,{\rm s}$. \ce{This timing is with \texttt{analysis}, it may be less without.}

	  Mean loss without regularisation for particles reproducing a target: $345 \pm 246$
  		\item For 100 runs with parameters
		\begin{equation}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 69\% & 11\% & 7\% & 12\% & 0\% & 4\% & 0\% & 13\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta5}.

@@

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_18_at_06_28_32.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_18_at_06_28_32_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta5}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta5}
	  \end{figure}

	  \item For 100 runs with parameters
		\begin{equation} \label{eq:sample10000beta3}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.1, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 76\% & 18\% & 10\% & 6\% & 4\% & 1\% & 2\% & 6\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3}.

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta3}
	  \end{figure}

	  \item For 100 runs with parameters
		\begin{equation} \label{eq:sample10000beta3sigmavar}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 68\% & 17\% & 6\% & 9\% & 2\% & 1\% & 1\% & 11\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3sigmavar}.

@@

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3sigmavar}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta3sigmavar}
	  \end{figure}

	  \item For 100 runs with parameters
		\begin{equation} \label{eq:sample1000}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 1000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 72\% & 27\% & 3\% & 19\% & 2\% & 0\% & 0\% & 12\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample1000}.

@@

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample1000}
	  \end{figure}
  \end{enumerate}

>>>>

  \begin{enumerate}
  		\item {\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample size} = 10000$}

	  For 100 runs with parameters
		\begin{equation} \label{eq:sample10000beta3}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.1, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 76\% & 18\% & 10\% & 6\% & 4\% & 1\% & 2\% & 6\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3}.

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{{\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta3}
	  \end{figure}

	  After the AIS, we performed an exploitation phase to fine tune the coefficients. The distributions of the particles with respect to their loss (without regularisation), is plotted in fig.~\ref{fig:distlocalsearch}. The fine tuning (with \texttt{local\_search}) is made using the loss with regularisation.

	  \begin{figure}[h!]
	  	\centering
	  	\includegraphics[scale=0.75]{Figures/Local_search_2025_05_19_at_06_01_21.pdf}
	  	\caption{{\bfseries \boldmath $\beta$ in power $3$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} Distributions of all the 100,000 particles with respect to their loss (without regularisation) (a) directly after AIS with parameters~\eqref{eq:sample10000beta3} and (b) after 200 steps of \texttt{local\_search}. The fine tuning (with \texttt{local\_search}) is made using the loss with regularisation.}
	  	\label{fig:distlocalsearch}
	  \end{figure}

	  We list below, for each polynomials in eq.~\eqref{eq:pols}, one example of representing particles directly after AIS and after the fine tuning, and the associated losses (without regularisation):
	  \begin{align}
	  	p_{1}:&\quad
	  	\begin{aligned}
	  		&-1.939\,x_{1} + 2.120\,x_{1}\tilde{x}_{8} + x_{10}x_{2}\tilde{x}_{8} - 2.266\, x_{2}x_{4}\tilde{x}_{8} + 0.029\,x_{2}^{2}x_{4},\quad L^{(\lambda = 0)} \simeq 754, \\
			&-1.416\,x_{1} + 1.414\, x_{1}\tilde{x}_{8} + x_{10}x_{2}\tilde{x}_{8} - 1.414\,x_{2}x_{4}\tilde{x}_{8} + 0.00001\,x_{2}^{2}x_{4},\quad L^{(\lambda = 0)} \simeq 0.0040,
	  	\end{aligned} \\[7pt]
	  	p_{2}:&\quad
	  	\begin{aligned}
	  		&2.213\,x_{2} - 2.075\,x_{2}\tilde{x}_{8} + 1.674\,x_{1}x_{10} + 2.015\,x_{1}x_{4} - x_{10}^{2}x_{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 244, \\
			&2.002\,x_{2} - 2.002\,x_{2}\tilde{x}_{8} + 1.417\,x_{1}x_{10} + 2.001\,x_{1}x_{4} - x_{10}^{2}x_{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 0.015,
	  	\end{aligned} \\[7pt]
	  	p_{3}:&\quad
	  	\begin{aligned}
	  		&2\,x_{2} - 1.808\,x_{2}\tilde{x}_{8} + 1.168\,x_{1}\tilde{x}_{8}x_{10} + 1.828\,x_{1}x_{4}\tilde{x}_{8} - 1.864\,x_{2}x_{4}^{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 180, \\
			&2\,x_{2} - 1.998\,x_{2}\tilde{x}_{8} + 1.412\,x_{1}\tilde{x}_{8}x_{10} + 1.998\,x_{1}x_{4}\tilde{x}_{8} - 1.998\,x_{2}x_{4}^{2}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 0.016,
	  	\end{aligned} \\[7pt]
	  	p_{4}:&\quad
	  	\begin{aligned}
	  		&1.458\,x_{2} - 1.341\,x_{2}\tilde{x}_{8} + 1.497\,x_{1}x_{4} + x_{1}\tilde{x}_{8}x_{10} - 1.008\,x_{2}x_{4}\tilde{x}_{8}x_{10} + 0.020 x_{2}^{2}x_{4}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 218, \\
			&1.419\,x_{2} - 1.418\,x_{2}\tilde{x}_{8} + 1.416\,x_{1}x_{4} + x_{1}\tilde{x}_{8}x_{10} - 1.001\,x_{2}x_{4}\tilde{x}_{8}x_{10} - 0.0003\,x_{2}^{2}x_{4}\tilde{x}_{8},\quad L^{(\lambda = 0)} \simeq 0.074,
	  	\end{aligned} \\[7pt]
	  	p_{5}:&\quad
	  	\begin{aligned}
	  		&-2.179\,x_{1} - 1.571\,x_{2}x_{4} - 1.953\,x_{1}x_{4}^{2} + 1.983\,x_{1}\tilde{x}_{8} + 1.530\,x_{2}x_{10} + x_{1}\tilde{x}_{8}x_{10}^{2},\quad L^{(\lambda = 0)} \simeq 210, \\
			&-2.008\,x_{1} - 2.001\,x_{2}x_{4} - 1.999\,x_{1}x_{4}^{2} + 1.995\,x_{1}\tilde{x}_{8} + 1.412\,x_{2}x_{10} + x_{1}\tilde{x}_{8}x_{10}^{2},\quad L^{(\lambda = 0)} \simeq 0.228,
	  	\end{aligned} \\[7pt]
	  	p_{6}:&\quad
	  	\begin{aligned}
	  		&- 2.856\,x_{2}x_{4} - 2.499\,x_{1}x_{4}^{2} + 2.721\,x_{2}x_{4}\tilde{x}_{8} + 1.677\,x_{2}x_{10} - 1.187\,x_{2}\tilde{x}_{8}x_{10} + x_{1}\tilde{x}_{8}x_{10}^{2} ,\quad L^{(\lambda = 0)} \simeq 202, \\
			&- 2.043\,x_{2}x_{4} - 2.005\,x_{1}x_{4}^{2} + 2.030\,x_{2}x_{4} \tilde{x}_{8} + 1.393\,x_{2}x_{10} - 1.401\,x_{2}\tilde{x}_{8}x_{10} + x_{1}\tilde{x}_{8}x_{10}^2 ,\quad L^{(\lambda = 0)} \simeq 1.28,
	  	\end{aligned} \\[7pt]
	  	p_{7}:&\quad
	  	\begin{aligned}
	  		&- 1.354\,x_{1}^{2}x_{4} + 1.243\,x_{2}^{2}x_{4} + 1.304\,x_{1}x_{2}x_{4}^{2} - 1.053\,x_{1}^{2}x_{10} - x_{2}^{2}x_{10} + 0.052\,x_{2}x_{4}^{2}x_{10} ,\quad L^{(\lambda = 0)} \simeq 373, \\
			&- 1.413\,x_{1}^{2}x_{4} + 1.415\,x_{2}^{2}x_{4} + 1.413\,x_{1}x_{2}x_{4}^{2} - 0.997\,x_{1}^{2}x_{10} - x_{2}^{2}x_{10} + 0.0003\,x_{2}x_{4}^{2}x_{10} ,\quad L^{(\lambda = 0)} \simeq 0.038.
	  	\end{aligned}
	  \end{align}

	  \item {\bfseries \boldmath $\beta$ in power $4$, $\sigma = 0.1$, $\texttt{sample size} = 10000$}

	  For 100 runs with parameters
		\begin{equation} \label{eq:sample10000beta4}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{4}, \quad \sigma = 0.1, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 74\% & 17\% & 7\% & 8\% & 2\% & 0\% & 2\% & 6\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta4}.

	  Averaged number of particles reproducing a target in a successful run: $951 \pm 200$

	  Mean loss with regularisation for particles reproducing a target: $709 \pm 320$

	  Mean loss without regularisation for particles reproducing a target: $452 \pm 309$

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_22_at_08_48_38.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_22_at_08_48_38_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{{\bfseries \boldmath $\beta$ in power $4$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta4}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta4}
	  \end{figure}

	  \item {\bfseries \boldmath $\beta$ in power $5$, $\sigma = 0.1$, $\texttt{sample size} = 10000$}

  		For 100 runs with parameters
		\begin{equation}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 69\% & 11\% & 7\% & 12\% & 0\% & 4\% & 0\% & 13\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta5}.

@@

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_18_at_06_28_32.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_18_at_06_28_32_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{{\bfseries \boldmath $\beta$ in power $5$, $\sigma = 0.1$, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta5}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta5}
	  \end{figure}

  		\item {\bfseries \boldmath $\beta$ in power $5$, $\sigma$ varying, $\texttt{sample size} = 10000$}

  		For 100 runs with parameters
		\begin{equation} \label{eq:sample10000beta5}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 59\% & 25\% & 5\% & 9\% & 2\% & 4\% & 2\% & 13\%
	  	\end{tabular}
	  \end{equation}
	  The sum of the percentages is higher than 100\% because some runs find more than one polynomials. The code fails to find any polynomial in 13\% of the time. The averaged time needed for a single run on a PC in $\sim 700\,{\rm s}$. \ce{This timing is with \texttt{analysis}, it may be less without.}

	  Mean loss without regularisation for particles reproducing a target: $345 \pm 246$

	  \item {\bfseries \boldmath $\beta$ in power $3$, $\sigma$ varying, $\texttt{sample size} = 10000$}

	  For 100 runs with parameters
		\begin{equation} \label{eq:sample10000beta3sigmavar}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 68\% & 17\% & 6\% & 9\% & 2\% & 1\% & 1\% & 11\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3sigmavar}.

@@

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{{\bfseries \boldmath $\beta$ in power $3$, $\sigma$ varying, $\texttt{sample size} = 10000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3sigmavar}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta3sigmavar}
	  \end{figure}

	  \item {\bfseries \boldmath $\beta$ in power $5$, $\sigma=0.1$, $\texttt{sample size} = 1000$}

	  For 100 runs with parameters
		\begin{equation} \label{eq:sample1000}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 1000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 72\% & 27\% & 3\% & 19\% & 2\% & 0\% & 0\% & 12\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample1000}.

@@

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{{\bfseries \boldmath $\beta$ in power $5$, $\sigma=0.1$, $\texttt{sample size} = 1000$} (a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample1000}
	  \end{figure}
  \end{enumerate}
